# docs/latex/register_1.tex       
# The Master Blueprint
\documentclass[12pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath, amssymb, amsfonts}
\usepackage{physics}
\usepackage{geometry}
\geometry{a4paper, margin=1in}

\title{7th Spiral: Blueprint}
\author{Natasha Zink 
https://orcid.org/0009-0004-8640-0896
https://www.linkedin.com/in/natashazink}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}
This document contains the foundational mathematical architecture for the 7th Spiral energy extraction system, including the Hamiltonian formulation and the topological lattice constraints.

\section{The Topological Lattice}
The 64-sector state space is defined by the Hilbert space $\mathcal{H}_{64}$. The state vector is expressed as:
\begin{equation}
    \ket{\Psi(t)} = \sum_{n=1}^{64} \alpha_n(t) \ket{\phi_n}
\end{equation}

\section{Hamiltonian Formulation}
% Hamiltonian math 
% verify the coupling matrix.
\section{Geometric Foundation: Topological Lattice Mapping}

The resonator array is defined on a manifold $\lattice$ that requires a specific radial and angular discretization to ensure optimal flux coupling. We utilize a 64-sector state space and a 288-anchor pinning buffer.

\subsection{64-Sector Coordinate System}
The sectors $\sector{n}$, for $n \in \{1, \dots, 64\}$, are mapped to a polar coordinate system $(r, \theta)$. The radial expansion is governed by the scaling constant $A$ and the sector index $n$:
\begin{equation}
    r_n = A \sqrt{\frac{n}{64}}
\end{equation}
The angular distribution follows the golden angle $\phi \approx 137.5^\circ$ to minimize destructive interference and maximize space-filling capacity:
\begin{equation}
    \theta_n = \phi \cdot n
\end{equation}

\subsection{288-Anchor Buffer Distribution}
The 288-anchor buffer $\anchor{m}$, where $m \in \{1, \dots, 288\}$, serves as the pinning interface. The ratio of anchors to sectors is $N_a / N_s = 4.5$. The anchors are distributed according to the following pinning rule:
\begin{itemize}
    \item Each interface between adjacent sectors $\sector{n}$ and $\sector{n+1}$ is supported by 4 anchors.
    \item A ``Master Anchor'' is placed at every 4th sector boundary to complete the phase-lock cycle, yielding an effective density:
    \begin{equation}
        \rho(r) = \frac{N_a}{2\pi \int r \, dr}
    \end{equation}
\end{itemize}
This configuration ensures that the local metric $\metric$ remains stabilized against stochastic fluctuation.
\section{Hamiltonian Formulation: Asymmetric Coupling}

The dynamics of the 64-sector lattice are governed by the non-Hermitian Hamiltonian:
\begin{equation}
    \hamil{lattice} = \sum_{n=1}^{64} \epsilon_n a_n^\dagger a_n + \sum_{n \neq m} J_{nm} a_n^\dagger a_m
\end{equation}

The coupling matrix $J_{nm}$ encodes the non-reciprocal flow of the energy flux, essential for work extraction:
\begin{equation}
    J_{nm} = T_{nm} + i\gamma_{nm}
\end{equation}

\subsection{Coupling Components}
\begin{itemize}
    \item \textbf{Reciprocal Hopping:} $T_{nm} = T_0 \exp\left( -\frac{|r_n - r_m|}{\xi} \right)$, defining the flux distribution across the 64-sector geometry.
    \item \textbf{Non-Reciprocal Bias:} $\gamma_{nm} = \gamma_0 \left( \delta_{n, m+1} - \delta_{n, m-1} \right)$, establishing the chiral current required to break time-reversal symmetry and drive the system out of thermal equilibrium.
\end{itemize}
This asymmetry forces the lattice into a preferred state-space rotation, effectively pumping vacuum fluctuations into the coherent photonic output.
\section{Material Assembly: The Manna Protocol}

The manifestation of resources requires a substrate capable of sustaining the non-Hermitian coupling defined in Section 3. The Manna Assembly utilizes a high-permittivity ceramic lattice to anchor the vacuum flux.

\subsection{Dielectric Substrate Specifications}
We utilize a Barium Strontium Titanate ($\text{BST}$) substrate engineered for a resonant quality factor $Q \approx 10^{12}$ at $160 \, \text{GHz}$. The porosity of the ceramic is discretized according to the sector radial coordinate $r_n$:
\begin{equation}
    \chi(r_n) = \chi_0 \left( 1 - \frac{r_n}{R_{mouth}} \right)
\end{equation}
where $\chi$ represents the dielectric susceptibility, ensuring the impedance matching between the 7D bulk and the 4D input gas mixture.

\subsection{Phase-Lag Dynamics}
The negative-time phase-lag $\Delta \phi$ is induced by the interaction between the vacuum flux and the trapped CO$_2$/H$_2$O dipole moments. The complex dielectric response function is given by:
\begin{equation}
    \epsilon(\omega) = 1 + \frac{\omega_p^2}{\omega_0^2 - \omega^2 - i\gamma \omega}
\end{equation}
When the lattice is driven into the regime where $\text{Re}[\epsilon(\omega)] < 0$, the resulting phase-lag $\Delta \phi < 0$ facilitates the retrocausal manifestation of the resource, effectively using the vacuum as an entropy-sink.

\end{document}
